---
title: "BAN-502-RRefresher"
author: "Adwoa Kessie"
date: "1/21/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# install.packages("tidyverse")
library(tidyverse)
```

```{r}
diamonddata = diamonds
print("Number of columns: ")
print(ncol(diamonddata))
print("Number of rows: ")
print(nrow(diamonddata))

```


```{r}
ggplot(data=diamonddata, aes(x=carat, y=price))  +
  geom_point() +
  labs(title = "Carat vs. Price", # plot title 
         x = "Carat", # x axis label 
         y = "Price" # y axis label 
  )
```

#### The relationship between Carat and Price is positive, meaning as the Carat increases, the Price increases as well. Also, it doesn't looks to be a linear increase. It looks like an exponential increase in price as Carat increases.


```{r}
ggplot(data=diamonddata, aes(x=carat, y=price, color=cut))  +
  geom_point() +
  labs(title = "Carat vs. Price", # plot title 
         x = "Carat", # x axis label 
         y = "Price" # y axis label 
  )
```

#### The diamonds with ideal cut increases in price very fast as the carat go up. I can see price going to maximum even with carat = 1.
#### With cut = 'fair', I see a linear increase in price as the carat increases. 
#### So, the price increase speed is fastest for 'ideal' cut and lowest for 'fair' cut.


```{r}
ggplot(data=diamonddata, aes(x=carat, y=price, color=cut))  +
  geom_point() + facet_grid(color ~ ., scales = "free", space = "free")
  labs(title = "Carat vs. Price", # plot title 
         x = "Carat", # x axis label 
         y = "Price" # y axis label 
  )
```
#### 1. I don't see many 'fair' cut diamonds in D color, while there are more 'fair' cut diamonds in G, H, I and J color.
#### 2. Most of the diamonds in D color no more than 2. But, For color G, H, I and J, I see diamonds going up to 3 carat.
#### 3. With color D, even low carat doamonds (1-2 carat) have high prices. But with color H, I and J, the price increase linearly and is maximum for diamonds with carat 2-3.

```{r}
inventory = read_csv("InventoryData.csv")
```

```{r}
inventoryA = filter(inventory, inventory$Supplier == 'A')
```

#### We have 3,695 rows with Supplier A.

```{r}
inventoryA = mutate(inventoryA, OnHandRatio = `On Hand`/ `Annual Demand`)
```

#### We used the mutate function to create a new column called 'OnHandRatio'


```{r}
avg_cost = inventory %>% 
  group_by(`Item SKU`) %>% 
  summarise (mean = mean(`Cost per Unit ($)`))
```


#### Working with 'lubridate' was challenging. Also, a little more understanding on Shiny R would be good.










