---
title: "Mod3Assign1"
author: "Adwoa Kessie"
date: "2/5/2022"
output: word_document
---

```{r }
library(tidyverse)
library(lubridate)
library(tidymodels)
```


```{r }
bike = read.csv('bike_cleaned-2.csv')
```

```{r}
bike = bike %>% mutate(dteday = mdy(dteday)) #mdy is a lubridate package function
```

```{r}
bike = bike %>% mutate_if(is.character, as_factor)
```

```{r}
bike = bike %>% mutate(hr = as_factor(hr))
```

```{r}
set.seed(1234)
bike_split = initial_split(bike, prop = 0.70, strata = count)
train = training(bike_split)
test = testing(bike_split)
```

## Training set has 12163 rows, test set has 5216 rows

```{r}
model = lm(count~season+mnth+hr+holiday+weekday+temp+weathersit, data=train)
summary(model)

```
## The model has Adjusted R2 of 0.6209. hr is a significant variable because all the hour values are significant. For month nd weekday, only a few values are significant.

```{r}
pred_train = predict(model, train)
pred_train_df = data.frame(pred_train)

```

```{r}

ggplot(pred_train_df, aes(x=pred_train)) + geom_histogram()

```

## The predicted values look to be normally distributed around 200 However, this is not perfectly normal distribution as there is a dip in the histogram right at the center.


```{r}
Rsquared = function (x, y) cor(x, y)^2
RsquaredTest = Rsquared(predict(model, test), test$count)

```

## Training model has R2 of 0.6209 and test has the R2 of 0.627 which are pretty close to each other. However, since in general, if the R2 of test > R2 of training, it might imply overfitting. In this case though, the difference is minimal.




