---
title: "Module2 MultiLinearRegression"
author: "Adwoa Kessie"
date: "1/30/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(tidymodels)
library(glmnet)
library(MASS)
library(ggcorrplot)
library(lubridate)
library(lmtest)
library(car)
```

```{r }
bike = read.csv('bike_cleaned.csv')
```

```{r}
bike = bike %>% mutate(dteday = mdy(dteday)) #mdy is a lubridate package function
```

```{r}
bike = bike %>% mutate_if(is.character, as_factor)
```

```{r}
bike = bike %>% mutate(hr = as_factor(hr))
```

# We convert hr to factor because integer values are considered continuous numbers and have priorities assigned. However, factors are categorical variables which do not have priorities.

```{r}
cor(bike[, c(10,11,12,13,16)])
```

# temp is the most correlated with count.

```{r}

ggplot(bike,aes(x=hr,y=count)) + geom_boxplot() + theme_bw()

```


```{r}

ggplot(bike,aes(x=season,y=count)) + geom_boxplot() + theme_bw()

```

Seasons affect count as Summer has the highest count, and winter has the lowest


```{r}

ggplot(bike,aes(x=mnth,y=count)) + geom_boxplot() + theme_bw()

```

#month affects count as I see that the count starts to increase from january until june, then stay around the same until aug, and then starts to decrease again.

```{r}

ggplot(bike,aes(x=holiday,y=count)) + geom_boxplot() + theme_bw()

```

# holiday affects count as 'not holiday' has higher count than 'holiday'.


```{r}

ggplot(bike,aes(x=weekday,y=count)) + geom_boxplot() + theme_bw()

```

#weekday dores not really affect count as the count are not very different for each weekday

```{r}

ggplot(bike,aes(x=workingday,y=count)) + geom_boxplot() + theme_bw()


```

# workingday also deoesnt seem to affect count very much. As the count is very close to each other for working and not working day

```{r}

ggplot(bike,aes(x=weathersit,y=count)) + geom_boxplot() + theme_bw()

```
#weathersit affects the count as NoPrecip has the higest count, while HeaveyPrecip has the lowest.

```{r}
model = lm(count~hr, bike)
summary(model)
```

#The model seem to show that each hr value is significant to predict the count.

```{r}
model = lm(count ~ . - instant - dteday - registered - casual, data = bike)
summary(model)
```
# In this model, a few values of variables weekday and month are not very significant based on their p-values. However this model is better than the one I created before which only used hr as the predictor variable. This is because the R square of this model = 0.63, while  my previous model = 0.50


# The variables temp and atemp are very highly correlated (0.98). Hence there is multicollinearity. So we can eliminate one of those variables from the model.


```{r}

model = lm(count ~ . - instant - dteday - registered - casual, data = bike)
step.model = stepAIC(model, direction = 'backward')
summary(step.model)

```

# After using backward stepwise model, there doesn't sem to be any change in the model efficiency as compared to ythe previous model in Step 5. I tried forward and both directions too, but the result was the same. I also manually removed 'atemp' and 'worday' variable as they seem to have multicollinearity, but that also did not imprive the model efficiency.












